\documentclass[../main.tex]{subfiles}

\begin{document}
These notes are intended for and written by a particular PhD student -- me. I do not expect to publish or use them as lecture notes. In fact, I don't even intend to read them in the future. I will occasionally make revisions, but that's all. Of course, the imaginary reader might ask why am I writing these notes. I want to accomplish at least two purposes. One is to improve my writing skills, and the other is to consolidate my knowledge -- as well as to learn new concepts -- of game theory. I clearly wouldn't be able to accomplish this goal alone, so I have the company of at least two books: \cite{OR} and \cite{FT}. I will mostly follow the former, but I will read the latter too. In order to succeed in this project, I will also follow this principle very rigorously: \say{Read the material, absorb it, summarize it, think, and then -- and only then --  write about it with your own words as best as you can}. I expect this task to take me about 3 months to conclude -- I obviously wrote this preface before starting the project.

I would also like to propose a pact. I am committed to making these notes as rigorous, detailed, and intellectually honest as possible. I am prohibited from simply throwing formulas, theorems, and demonstrations without a satisfactory explanation of what they mean. It is also prohibited to go astray from the big picture. Have in mind what the goal is here: to explain the set of tools in game theory, reflecting upon the fundamental questions and meanings of this topic.

The notes not only contain comments and detailed definitions, proofs, and examples, but also many exercises with solutions, which I select from \cite{OR} and \cite{FT}.
\end{document}